Eagle: multi-locus association mapping on a genome-wide scale made routine

### 2019-07-28 BioinformaticsRevison/bioinformaticspaper.tex
Working of Generating simulated data section git push

The data are generated via data perturbation \citep{zhao2007arabidopsis}. 
Data perturbation amalgamates real with simulated data to generate replicates. 
It is a way of introducing greater realism into a simulation study. 
 Here, the genotype data are real, the 
quantitative trait data are simulated. 
 The SNP genotypes are drawn, 
according to the specifications of the scenario , from data collected from the 1000 Genome Project, version 3   \citep{10002010map}. 
Across scenarios (see Results for details), the SNP data differs. Across replicates within a scenario, the SNP data are the same. For each scenario, 100 replicates are generated.

@@

There is no need to tune the regularisation parameter for bigRR as an optimal value is found as part of its analysis. 
As described above, we draw 100 replicate subsets of size $n/2$ and analyse these data with bigRR. We then order the 
SNPs according to the absolute size of their SNP effects and record the top 20 SNPs. 
A (probability)  estimate of the statistical significance of a SNP effect is then obtained by counting the 
number of times the SNP is recorded divided by the number of replicates.

>>>>

The data are generated via data perturbation \citep{zhao2007arabidopsis}. 
Data perturbation amalgamates real with simulated data to generate replicates. 
It is a way of introducing greater realism into a simulation study. 
 Here, the genotype data are real, the 
quantitative trait data are simulated. 
 The SNP genotypes are drawn, 
according to the specifications of a particular simulation scenario , from data collected from the 1000 Genome Project, version 3   \citep{10002010map}. Six different scenarios are considered. These scenarios differ in  their sample size and number of 
SNPs (see Results for details).  Here, across scenarios, the SNP data differs. Across replicates within a scenario, the SNP data are the same. For each scenario, 100 replicates are generated.

@@
